---
title: "Package Tutorial"
author: "Anna Lander"
date: "`r Sys.Date()`"
output: html_document
---


#An introduction to my R package

This R package is designed to analyze data from years of amphibian species collection at a North Dakota site. Multiple amphibian species were collected from this location during the summer months between 2001 and 2013. This data has multiple questions that can be answered in this data set, and some of the functions within this package can help us form testable hypotheses of the given data. 

#Installing the R Package GBIO.Final

To install this package, enter the following code into your R console. This package will include functions from tidyverse, as well as original functions.

```{r}

install.packages("remotes")
library(remotes)

install.packages("tidyverse")
library(tidyverse)

install.packages("ggplot2")
library(ggplot2)


```
```{r}
remotes::install_github("annalander/lander_pck")
install.packages("GBIO.Final")
library(GBIO.Final)
```


#Downloading data for package

Once you have downloaded the data, save it to a data frame called "AGP", this will be used for some of the functions. 

```{r eval=FALSE, include=TRUE}
download.file(url = "https://raw.githubusercontent.com/annalander/lander_pck/master/Data/AGP%2Bfield%2Bdata%2Bcopy.csv", destfile = "/cloud/project/Data/AGP+field+data+copy.csv")

AGP <- read_csv("/cloud/project/Data/AGP+field+data+copy.csv")
```



#Functions in this Package: How to use them

##Hist

This function creates a histogram of size classes for each amphibian collected in this data set.

```{r,eval=FALSE}

histogram <- function(AGP){
     AGP_hist <- ggplot(data = AGP, mapping = aes(x = svl)) + geom_histogram() + labs(title = "Snout-Vent Length in Amphibians", x = "Snout-Vent Length (mm)", y = "Number of Individuals") + xlim(0, 150)
     return(AGP_hist)
}

histogram(AGP)

```


##LinMod

This function runs a linear model on the mass and snout-vent length of collected amphibian species. 

```{r,eval=FALSE}

lin_model <- function(filepath){
     AGP_raw <- read_csv("/cloud/project/Data/AGP+field+data+copy.csv")
     lin_data <- AGP_raw
     model_fit <- lm(mass ~ svl, data = lin_data)
     return(summary(model_fit))
}

lin_model("/cloud/project/Data/AGP+field+data+copy.csv")

```


##NoNA

This function is designed specifically to clear NA values from the given data set for better interpretation of data. The AGP data set contains NA values for some important columns (like svl and mass)

```{r,eval=FALSE}

nona <- function(filepath){
  data_na <- read_csv(filepath)
  data_nona <- data_na %>% 
    na.omit()
  return(data_nona)
}

nona("/cloud/project/Data/AGP+field+data+copy.csv")

```


##LinModPlot

This function will allow you to visualize the relationship of the mass of the collected amphibian specimens and the snout-vent length (SVL).

```{r,eval=FALSE}

point_plot <- function(critter){
  AGP %>% 
    filter(critter == "Tiger Salamander") 
  AGPpoint <- ggplot(data = AGP, mapping = aes(x = svl, y = mass, color = stage)) + geom_point() + xlim(0,150) + ylim(0,150) + labs(title = "Relationship Between Mass and Snout-Vent Length in Amphibians", x = "Snout-Vent Length (mm)", y = "Mass (g)")
  return(AGPpoint)
}

point_plot(AGP)

```


##Clean

This function pulls specific columns from the amphibian data set (critter, svl, mass, and stage) and creates a data frame that can be utilized for other functions. Use the filepath where you stored the function to run this function. 

```{r,eval=FALSE}

data_cleaning <- function(filepath){
  AGP_clean <- read_csv("/cloud/project/Data/AGP+field+data+copy.csv") %>% 
    select(critter, svl, mass, stage)
  return(AGP_clean)
}

data_cleaning(AGP)

```

